Covering Your Basis: Model Agnostic Probes of the Binary Black Hole Population

### 2022-09-27 src/tex/appendicies.tex
Update readme with current tasks / progress

Spline functions have been shown to be sensitivite to the chosen number of knots, and their locations or spacing \citep{deBoor78}. 
Adding more knots knots increases the a-priori variance in the spline function, while the space between knots can limit the 
resolution of features in the data the spline is capable of resolving. To ensure your spline based model is flexible enough 
one would want to add as many knots as densely as possible, but this comes with the inherit larger variance as mentioned above. 
To overcome this we resort to the frequentist penalized spline (P-Spline) in which one applies a penalty or regularization term 
to the likelihood based on the difference of adjacent knot coeficients \citep{eilers2021practical}. The linear combination of spline basis components 
or the resulting spline function is flat when the basis coeficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as 
the differences between adjacent knot coeficients get larger, one gets a smoothing of the spline function inferences \citep{eilers2021practical}. 
Since we are using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog. 
The difference penalty is equivalent to applying a stochastic differnece prior among the knots, as described in  \\citet{BayesianPSplines,Jullion2007RobustSO}. 
This is also sometimes referred to as a Gaussian random walk prior, since each coeficient is normally distributed about its neighboring coeficients. 
For a spline basis with $n$ degree's of freedom, and a difference penalty of order of $r$ (see \citet{eilers2021practical}), the smoothing prior is defined as:

@@

\section{Validation Studies} \label{sec:validation}

\bruce{Need to fill this section}

>>>>

Spline functions have been shown to be sensitivite to the chosen number of knots, and their locations or spacing \citep{deBoor78}. 
Adding more knots knots increases the a-priori variance in the spline function, while the space between knots can limit the 
resolution of features in the data the spline is capable of resolving. To ensure your spline based model is flexible enough 
one would want to add as many knots as densely as possible, but this comes with the inherit larger variance as mentioned above. 
To overcome this we resort to the frequentist penalized spline (P-Spline) in which one applies a penalty or regularization term 
to the likelihood based on the difference of adjacent knot coeficients \citep{eilers2021practical}. The linear combination of spline basis components 
or the resulting spline function is flat when the basis coeficients are equal (see Figure \ref{fig:spline_basis}). By penalizing the likelihood as 
the differences between adjacent knot coeficients get larger, one gets a smoothing of the spline function inferences \citep{eilers2021practical}. 
Since we are using hierarchical Bayesian inferece as our statistical framework, we formulate this penalized likelihood with its Bayesian analog. 
The difference penalty is equivalent to applying a stochastic differnece prior among the knots, as described in \citet{BayesianPSplines} and \citet{Jullion2007RobustSO}. 
This is also sometimes referred to as a Gaussian random walk prior, since each coeficient is normally distributed about its neighboring coeficients. 
For a spline basis with $n$ degree's of freedom, and a difference penalty of order of $r$ (see \citet{eilers2021practical}), the smoothing prior is defined as:

@@

%\section{Validation Studies} \label{sec:validation}

%bruce{Need to fill this section}
